---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages and data

```{r}
# Install/load packages
pacman::p_load(here,
               rio,
               brms,
               tidyr,
               MetBrewer,
               ggdensity,
               cmdstanr,
               bayesmeta,
               tidybayes,
               posterior,
               tidyverse,
               metafor,
               gt)

# Load death data
d1 = import(here("data", "tpa.xlsx")) |> 
  transform(outcome = "death")

# Load bleeding data
d2 = import(here("data", "tpa2.xlsx")) |> 
  transform(outcome = "bleed")

d = rbind(d1, d2)

```

Estimate log risk ratios

```{r}
d_logRR = 
  metafor::escalc(
  measure = "OR", # log odds ratio,
  
  # tPA
  ai = r2,
  n1i = n2,
  
  # AC
  ci = r1,
  n2i = n1,
  
  data = d
)
```

Construct a variance-covariance matrix assuming within-study correlation = $0.5$ 

```{r}

V = metafor::vcalc(vi, cluster=study, type=outcome, rho=0.5, data=d_logRR)

```

Fit a Bayesian bivariate meta-analysis. Further methodological details in
[Burke et al. 2016](https://journals.sagepub.com/doi/10.1177/0962280216631361).

```{r}
# Specify formula
mf = 
  brms::bf(yi ~ 0 + outcome + (0 + outcome|study) + fcor(V))

get_prior(mf, 
          data = d_logRR,
          data2 = list(V = V),
          family = gaussian)
```

Extract informative priors for between-study heterogeneity from [Turner et al. 2014](https://onlinelibrary.wiley.com/doi/10.1002/sim.6381)

```{r}
tau_death = bayesmeta::TurnerEtAlPrior("all-cause mortality",
                                       "pharmacological",
                                       "placebo / control")

bleed_death = bayesmeta::TurnerEtAlPrior("adverse events",
                                         "pharmacological",
                                         "placebo / control")

logmean_death = tau_death$parameters["tau", "mu"] # -1.975 
logsd_death = tau_death$parameters["tau", "sigma"] # 0.67

logmean_bleed = bleed_death$parameters["tau", "mu"] # -0.935 
logsd_bleed = bleed_death$parameters["tau", "sigma"] # 0.76


```

Define priors (weakly informative for treatment effects, informative 
for between-study heterogeneities, and weakly informative for the correlation parameters)

```{r}
priors = 
  prior(normal(0, 0.75), class = "b", coef = "outcomedeath") +
  prior(normal(0, 0.75), class = "b", coef = "outcomebleed") +
  prior(lognormal(-1.975, 0.67), class = "sd", coef = "outcomedeath", group = "study") +
  prior(lognormal(-0.935, 0.76), class = "sd", coef = "outcomebleed", group = "study") +
  prior(lkj(2), class = cor) +
  prior(constant(1), class = "sigma")
```

Fit model

```{r}

m1 = brms::brm(
  formula = mf,
  prior = priors,
  data = d_logRR,
  data2 = list(V = V),
  family = gaussian,
  
  warmup = 2000, 
  iter = 4000,
  chains = 4,
  cores = parallel::detectCores(),
  seed = 123,
  backend = "cmdstanr",
  
  file = here::here("model", "m1.Rds"),
  file_refit = "on_change"
)

```

```{r}
parameters = 
  m1 |> 
  tidy_draws() |> 
  reframe("ATE: Death" = b_outcomedeath,
          "ATE: Major Bleeding" = b_outcomebleed,
            
          "Tau: Death" = sd_study__outcomedeath,
          "Tau: Major Bleeding" = sd_study__outcomebleed,
            
          "Correlation" = cor_study__outcomebleed__outcomedeath) |> 
  pivot_longer(everything()) |> 
  group_by(name) |> 
  median_hdi(value) |> 
  mutate(across(value:.upper, ~round(., 2))) |> 
  select(-c(.width:.interval))

parameters |> 
  filter(str_detect(name, "ATE")) |> 
  mutate(across(-name, ~round(exp(.), 2))) |> 
  reframe(Parameter = name, 
          "Median [95% CrI]" = str_c(value, " [", .lower, ", ", .upper, "]")) |> 
  
  rbind(
    parameters |> 
    filter(str_detect(name, "ATE", negate = T)) |> 
    reframe(Parameter = name, 
            "Median [95% CrI]" = str_c(value, " [", .lower, ", ", .upper, "]"))
  ) |> 
  gt()
```

ATE = average treatment effect (linear scale)
Tau = Between-study variance (log scale)

Let's visualize the bivariate distribution of both ATEs.

```{r}
m1 |> 
  tidybayes::tidy_draws() |> 
  ggplot() +
  aes(x = b_outcomedeath, b_outcomebleed) +
  ggdensity::geom_hdr(
    probs = c(0.95, 0.8, 0.5),
    aes(fill = after_stat(probs)), 
    alpha = 1
  ) +
  scale_fill_manual(values = met.brewer("OKeeffe2", 3)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
  scale_x_continuous(breaks = log(c(0.25, 0.75, seq(0.5, 1.5, 0.5))),
                     labels = c(0.25, 0.75, seq(0.5, 1.5, 0.5))) +
  
  scale_y_continuous(breaks = log(c(0.5, seq(1, 4, 1))),
                     labels = c(0.5, seq(1, 4, 1))) +
  coord_cartesian(x = log(c(0.25, 1.6)),
                  y = log(c(0.5, 4.5))) +
  labs(x = "Odds Ratio (death)",
       y = "Odds Ratio (major bleeding)") +
  ggdist::theme_ggdist()
```

Bivariate analyses allow one to ask conditional probabilities, such as:

What is the posterior probability that...

- OR_death < 1.0 AND OR_bleeding < 1.0? (q1)

- OR_death < 1.0 AND OR_bleeding > 1.0? (q2)

- OR_death < 1.0 AND OR_bleeding > 2.0? (q3)

- OR_death > 1.0 AND OR_bleeding > 1.0? (q4)

```{r}
m1 |> 
  tidybayes::tidy_draws() |> 
  reframe(q1 = mean(b_outcomedeath < log(1) & b_outcomebleed < log(1)),
          q2 = mean(b_outcomedeath < log(1) & b_outcomebleed > log(1)),
          q3 = mean(b_outcomedeath < log(1) & b_outcomebleed > log(2)),
          q4 = mean(b_outcomedeath > log(1) & b_outcomebleed > log(1))) |> 
  gt()
```

